\todo{Eric}{Please proof read}{}
The \ac{astroCAST} is a novel solution to a longstanding challenge in neuroscience research: the specialized analysis of astrocytic calcium events within fluorescence time-series imaging. Distinguished from existing neuron-centric tools, \ac{astroCAST} is adept at detecting and clustering astrocytic calcium events based on their unique spatiotemporal characteristics, thus filling a gap in astrocytic research methodologies. This toolkit not only facilitates the detection of such events but also extends its utility to provide comprehensive end-to-end analysis, a feature absent in most astrocyte-focused tools. \ac{astroCAST}'s development was motivated by the critical need for dedicated software that supports researchers in transitioning from raw video data to insightful experimental conclusions, efficiently managing large-scale datasets without compromising computational speed. It offers a user-friendly interface that caters to both novice and expert users, incorporating both a \ac{GUI} for detailed explorations and a \ac{CLI} for handling extensive analyses. Expected outcomes from utilizing \ac{astroCAST} include the ability to process and analyze a significantly larger volume of data. This capability enables a more profound and comprehensive analysis than previously possible, addressing the demands of large-scale astrocytic studies. In summary, \ac{astroCAST} represents a significant step forward in astrocytic calcium imaging analysis, offering a tailored, efficient, and comprehensive toolset that enhances our understanding of astrocytic functions and their implications in neuroscience.