\newpage

\section*{TODOs}

\todo{Jan}{Code sections}{
\begin{itemize}
    \item \sout{reformat color coding of YAML style}
    \item \sout{check all inline code references for appropriate format}
\end{itemize}
}

\todo{Jan}{Content}{
\begin{itemize}
    \item \sout{Add section to methods how to use the SignalGenerator class}
    \item Add section to methods which module uses what kind of packages
    \item \sout{Table with encoding requirements}
    \item move some sections to Methods (downloading datasets, dataset showcase, downloading pretrained models)
    \item Somewhere we need to discuss the Pro's and Con's of the different experiment modules: pearson correlation sucks; dtw is great for variable length, but slow and slightly underperforms on fixed length; CNN is fast and good, but can't be used for fixed length; FExt is fast and easy, but underperforms on complex event types; RNN is slow but powerful, but hard to finetune.
\end{itemize}
}

\todo{Jan}{Figures}{
    \begin{itemize}
        \item Update Figure 1: Adjust the graphical abstract to better reflect recent changes, possibly including distinctions between Supervised and Unsupervised learning approaches to enhance clarity for the reader.
        \item Combine Figures 2 and 3: Consider merging these figures to streamline the presentation and reduce redundancy, ensuring a coherent narrative flow.
        \item Adjust Figure 4 for enhanced readability:
        \begin{itemize}
            \item Implement a new color order: red, turquoise, purple, green, to improve visual distinction between elements.
            \item Standardize the x-axis label across similar plots to maintain consistency and ease of understanding.
            \item Label panels A and B clearly to guide the reader through the figure seamlessly.
            \item Annotate image pixels with the color of the trace in panels A and B to directly link visual data with its analytical representation, enhancing interpretability.
            \item Rearrange sub-panels to preserve a logical flow, with row 1 showing conditions before subtraction and row 2 showing conditions after subtraction, to logically guide the reader through the data transformation process.
        \end{itemize}
        \item For Figure 5, implement color coding for the dots to provide a clearer, more immediate understanding of the data categories or values represented, facilitating quicker data interpretation.
        \item In Fig. 6C the algorithms are not working as expected. Specifically, the classifier overperforms (correctly classifying the identical dataset), while the regression underperforms (no correct predictions in any condition).
    \end{itemize}
}

\todo{Jan}{Very last checks}{
    \begin{itemize}
        \item \sout{convert tables to appropriate format}
        \item \sout{Fix logo and title overlap}
        \item proof read author names and affiliations
        \item check word count, manuscript length and figure number
        \item check supplementary material
        \item check all in-document references point to the correct section
        \item proof read 1
        \item get green light from all authors
        \item final proof read
    \end{itemize}
}

\newpage